Optimal Sizing of Stand-alone Solar PV Systems via Automated Formal Synthesis

### 2020-05-02 Tex/IEEE_TOSE/trindade_IEEETOSE_rev1.tex
removed basic stuff of MC
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

Although simulation and testing explore possible behaviors and scenarios of a given system, they leave open the question of whether new trajectories may contain a flaw. Formal verification conducts an exhaustive exploration of all possible behaviors; when a design is said to be ``correct'' by a formal verification method, it implies all behaviors explored, and questions regarding adequate coverage or missed behavior become irrelevant~\cite{Clarke2012}. Formal verification is a systematic approach that applies mathematical reasoning to obtain guarantees about the correctness of a system; one successful method in this domain is \textit{model checking}~\cite{Clarke2012}.

>>>>

%Although simulation and testing explore possible behaviors and scenarios of a given system, they leave open the question of whether new trajectories may contain a flaw. Formal verification conducts an exhaustive exploration of all possible behaviors; when a design is said to be ``correct'' by a formal verification method, it implies all behaviors explored, and questions regarding adequate coverage or missed behavior become irrelevant~\cite{Clarke2012}. Formal verification is a systematic approach that applies mathematical reasoning to obtain guarantees about the correctness of a system; one successful method in this domain is \textit{model checking}~\cite{Clarke2012}.
